State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements thus allowing the positioning of sensor in accordance to \ref{eq:MinimumSensorDistance}. However, we envisage it may be possible to estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}. Nevertheless, using electrophysiological measurements, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensor's spectral characteristics. Sensors with smooth wide spatial responses result in a spectral low-pass action, thus providing spatial anti-alaising filtering. Such sensors therefore bandlimit the field to a known bandwidth, denoted by $\nu_{co}$. Aliasing can then be avoided by positioning the sensors according to \ref{eq:MinimumSensorDistance}, with $\nu_{co}$ replacing $\nu_c$.

Although such sensors avoid errors due to alaising, they attentuate the high frequency variations in the observations. Therefore, any procedure applied to estimate the original field or the kernel from these bandlimited observations will underestimate the high frequency component in both the field and the kernel. Such a remark motivates the use of sensors with wider bandwidths. Nevertheless, this choice would require an excessive number or sensors in order to satisfy Shannon's sampling theorem for a reasonable spatial region. Therefore, a compromise needs to be found between the bandwidth of the sensor response and therefore the accurate of the estimation results and the number of sensors used and thus the computational demands of estimation procedure.

>>>>

In practice, it is difficult to estimate the bandwidth of the cortex using traditional electrophysiological measurements thus allowing the positioning of sensor in accordance to \ref{eq:MinimumSensorDistance}. However, we envisage it may be possible to estimate it using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques~\cite{Issa2000}. Nevertheless, using electrophysiological measurements, spectral aliasing can still be avoided by a proper choice of the spatial sampling distance given the sensor's spectral characteristics. Sensors with smooth wide spatial responses result in a spectral low-pass action, thus providing spatial anti-aliasing filtering. Such sensors therefore bandlimit the field to a known bandwidth, denoted by $\nu_{co}$. Aliasing can then be avoided by positioning the sensors according to \ref{eq:MinimumSensorDistance}, with $\nu_{co}$ replacing $\nu_c$.

Although such sensors avoid errors due to aliasing, they attenuate the high frequency variations in the observations. Therefore, any procedure applied to estimate the original field or the kernel from these bandlimited observations will underestimate the high frequency component in both the field and the kernel. Such a remark motivates the use of sensors with wider bandwidths. Nevertheless, this choice would require an excessive number or sensors in order to satisfy Shannon's sampling theorem for a reasonable spatial region. Therefore, a compromise needs to be found between the bandwidth of the sensor response and therefore the accurate of the estimation results and the number of sensors used and thus the computational demands of estimation procedure.
